A holomorphic approach to membranes and fivebranes

### 2022-06-03 fivebranes/index.tex
outline

Without loss of generality we will assume our holomorphic-topological local Lie algebra on $M \times X$ is of the form
\[
\cL = \Omega^\bu (M) \hotimes \Omega^{0,\bu}(X, L) 
\]
where $L$ is a graded holomorphic vector bundle on $X$.

\begin{lem}
\label{lem:localops}
Suppose that $\cL$ is a holomorphic-topological local Lie algebra on $\R^m \times \C^n$ and consider the factorization algebra $\Obs = \clie^\bu (\cL)$. 
Then, the Taylor expansion map
\[
\cL(\C^n \times \R^m) \to L_0[[z_0,\ldots,z_n]]
\]
induces a quasi-isomorphism of commutative dg algebras
\[
\Obs(0) \simeq \clie^\bu \left( L_0[[z_1,\ldots,z_n]] \right) .
\]
\end{lem}

@@

Suppose that $V$ is a translation invariant holomorphic vector bundle on $\C^n$ equipped with a $\Z \times \Z/2$ bigrading. 
Let $\cV$ denote its sheaf of holomorphic sections.
The {\em space of fields} of a holomorphic field theory on $\C^n$ is the $\Z \times \Z/2$ graded complex of vector bundles
\[
\Omega^{0,\bu}(\C^n, V) \cong \Omega^{0,\bu}(\C^n) \otimes V_0 
\]
where $V_0$ is the fiber of $V$ at $0 \in \C^n$.
Our grading conventions are so that $\d \zbar_i$ has bidegree $(1,0)$.

As introduced in \cite{BWhol,LiVertex,CG2}, a {\em holomorphic field theory} is a holomorphic vector bundle $V$ as above equipped additionally with:
\begin{itemize}
\item The structure of a local (super) $L_\infty$ algebra on $V[-1]$ with structure maps given by holomorphic polydifferential operators
\[
[\cdot]_k \colon \cV[-1]^{\times k} \to \cV[1-k] .
\]
\end{itemize}
A {\em free} holomorphic theory has $[\cdot]_k = 0$ for $k > 1$.

@@

\begin{eg}
Suppose that $V$ is the trivial bundle on $\C^n$. 
Then, the space of local operators is the symmetric algebra on the topological vector space which is linear dual to 
\[
\cO^{hol}(\Hat{D}^n) = \C[[z_1,\ldots,z_n]] .
\]
Via the $n$-dimensional residue one can identify the algebra of local operators with 
\[
\Sym\left(\frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n}  \C[z_1^{-1}, \ldots , z_n^{-1}]\right) .
\]

Consider the standard torus action $\C^\times \times \cdots \C^\times$ on $\C^n$. 
The equivariant character of local operators with respect to this symmetry is given by the plethystic exponential of the following `single particle index'
\[
\frac{1}{(1-q_1)\cdots (1-q_n)} .
\]
\end{eg}

@@

The theory on a single fivebrane is free and the underlying cochain complex of fields on $\C^3$ is given by 
\beqn
\begin{tikzcd}
\ul{-1} & \ul{0} \\
\Omega^{2,\bu}(\C^3) \ar[r,"\del"] & \Omega^{3,\bu}(\C^3) \\
\Pi \Omega^{0,\bu}(\C^3, K_{\C^3}^{1/2} \otimes \C^2) . 
\end{tikzcd} 
\eeqn
Here we recall the $\Z \times \Z/2$ bigrading where the differential has bidegree $(1,0)$.

\begin{lem}
\label{lem:single}
The $\Z/2$ algebra of local operators of the holomorphic single fivebrane theory is quasi-isomorphic to the graded symmetric algebra on the linear dual of the topological vector space
\beqn\label{eqn:localfree}
\Pi \Omega^{2,hol}_{cl} (\Hat{D}^3) \oplus \Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2 .
\eeqn
\end{lem}

@@

In \cite{SW6d} a symmetry by the exceptional super Lie algebra $E(3|6)$ on the holomorphic twist of the free tensor multiplet was constructed.
We recall the action of its even part on local operators of the holomorphic twist of the free tensor multiplet. 
We recount how it acts on the vector space \eqref{eqn:localfree}.

Recall that the even part of $E(3|6)$ consists of two summands:
\[
\Vect(\Hat{D}^3) \times \lie{sl}(2) \otimes \cO(\Hat{D}^3) .
\]
Formal vector fields act naturally by Lie derivative on both summands in \eqref{eqn:localfree}. 
An $\lie{sl}(2)$-valued function acts on $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$ where we view $\C^2 = {\rm span}\{r_+,r_-\}$ as the fundamental $\lie{sl}(2)$ representation.

We consider the equivariant character of local operators on the holomorphic twist of a single fivebrane with respect to the following finite dimensional subalgebra of $E(3|6)$ 
\[
\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset E(3|6) 
\]
which embeds in the following way: 
\begin{itemize}
\item The Lie algebra $\lie{sl}(3)$ is a subalgebra of $\Vect(\Hat{D}^3)$ consisting of linear coefficient vector fields $\sum_{i,j} a_{ij} z_i \frac{\del}{\del z_j}.$
where $(a_{ij}) \in \lie{sl}(3)$. 
\item The Lie algebra $\lie{sl}(2)$ is the subalgebra of $\lie{sl}(2) \otimes \cO(\Hat{D}^3)$ consisting of constant formal series. 
\item The one-dimensional Lie algebra $\lie{gl}(1)$ is spanned by Euler vector field $\sum_i z_i \frac{\del}{\del z_i} \in \Vect(\Hat{D}^3).$
\end{itemize}

@@

>>>>

@@

In this paper we are interested in theories obtained from twists of supersymmetric theories. 
Generally speaking, such twists have a mixed holomorphic and topological behavior.
%Suppose that $V$ is a translation invariant holomorphic vector bundle on $\C^n$ equipped with a $\Z \times \Z/2$ bigrading. 
%Let $\cV$ denote its sheaf of holomorphic sections.
%The {\em space of fields} of a holomorphic field theory on $\C^n$ is the $\Z \times \Z/2$ graded complex of vector bundles
%\[
%\Omega^{0,\bu}(\C^n, V) \cong \Omega^{0,\bu}(\C^n) \otimes V_0 
%\]
%where $V_0$ is the fiber of $V$ at $0 \in \C^n$.
%Our grading conventions are so that $\d \zbar_i$ has bidegree $(1,0)$.
%
%As introduced in \cite{BWhol,LiVertex,CG2}, a {\em holomorphic field theory} is a holomorphic vector bundle $V$ as above equipped additionally with:
%\begin{itemize}
%\item The structure of a local (super) $L_\infty$ algebra on $V[-1]$ with structure maps given by holomorphic polydifferential operators
%\[
%[\cdot]_k \colon \cV[-1]^{\times k} \to \cV[1-k] .
%\]
%\end{itemize}
%A {\em free} holomorphic theory has $[\cdot]_k = 0$ for $k > 1$.
%
%\parsec

Without loss of generality we will assume our holomorphic-topological local $L_\infty$ algebra on $M \times X$ is of the form
\beqn\label{eqn:cL}
\cL = \Omega^\bu (M) \hotimes \Omega^{0,\bu}(X, L) 
\eeqn
where $L$ is a graded holomorphic vector bundle on $X$.
The structure maps of the local $L_\infty$ algebra are required to be given by holomorphic polydifferential operators. 
For more details we refer to the definitions in \cite{GRWthf}.

In part, the data of a holomorphic-topological theory in the BV formalism is prescribed by a holomorphic-topological local $L_\infty$ algebra. 
The factorization algebra of classical observables supported on an open set $U \subset M \times X$ is given by the Chevalley--Eilenberg cochain on the $L_\infty$ algebra $\cL(U)$. 
We will give a concise presentation for the {\em local} operators in a topological-holomorphic theory.

Suppose that $M \times X = \R^m \times \C^n$ and suppose that the bundle $L \to \C^n$ is translation invariant with fiber $L_0$ over $0 \in \R^m \times \C^n$.
We also assume that all structure maps of the $L_\infty$ algebra are translation invariant.
The jet expansion at $0 \in \R^m \times \C^n$ determines a map of $L_\infty$ algebras
\[
\cL(\C^n \times \R^m) \to L_0 [[x_i, \d x_i,z_j, \zbar_j, \d \zbar_j]] 
\]
The differential, or one-ary, operation of the $L_\infty$ algebra on the right hand side is $\d_{dR} + \dbar + Q^{hol} = \d x_i \del_{x_i} + \d \zbar_j \del_{\zbar_j} + Q^{hol}$ where $Q^{hol}$ is some holomorphic differential operator in the $z_j$ variables. 
Since all structure maps are given by holomorphic polydifferential operators, the canonical map 
\[
L_0 [[x_i, \d x_i,z_j, \zbar_j, \d \zbar_j]] \xto{\simeq} L_0 [[z_j]] 
\]
is a quasi-isomorphism. 
The only remaining differential on the right hand side is~$Q^{hol}$. 
In total, the jet expansion at $0 \in \R^m \times \C^n$ determines a map of $L_\infty$ algebras $\cL(\R^m \times \C^n) \to L_0[[z_j]]$.

\begin{lem}
\label{lem:localops}
Suppose that $\cL$ is a holomorphic-topological local Lie algebra on $\R^m \times \C^n$ and consider the factorization algebra $\Obs = \clie^\bu (\cL)$. 
Then, the Taylor expansion map
\[
\cL(\C^n \times \R^m) \to L_0[[z_0,\ldots,z_n]]
\]
induces a quasi-isomorphism of commutative dg algebras
\[
\Obs(0) \simeq \clie^\bu \left( L_0[[z_1,\ldots,z_n]] \right) .
\]
Notice that when $\cL$ is abelian with differential $\d_{dR} + \dbar + Q^{hol}$, then there is a quasi-isomorphism
\[
\Obs(0) \simeq \cO \left( L_0[[z_1,\ldots,z_n]][1] \right) 
\]
where the right hand side is equipped with the differential $Q^{hol}$. 
\end{lem}

We recall the reader of the standard dictionary between the space of fields of a BV theory and the local $L_\infty$ algebra---
if the local Lie algebra is $\cL$, then the space of fields is $\cL[1]$. 
The Chevalley--Eilenberg complex of $\cL$ is then functions on the fields $\cO(\cL[1])$ equipped with the non-linear BRST operator.

\parsec[s:pexp]

\brian{characters, plethystic, etc.}

@@

We present some simple examples.

\begin{eg}
Suppose that $L$ is the trivial bundle on $\C^n$ and consider the abelian holomorphic-topological local Lie algebra 
\[
\Omega^\bu(\R^m) \otimes \Omega^{0,\bu}(X) [-1]
\]
where the differential is just $\d_{dR} + \dbar$. 
Notice that with the shift functions on $\R^m \times \C^n$ are in cohomological degree $+1$.
Then, the space of local operators is the symmetric algebra on the topological vector space which is linear dual to 
\[
\cO^{hol}(\Hat{D}^n) = \C[[z_1,\ldots,z_n]] .
\]
Via the $n$-dimensional residue one can identify the algebra of local operators with 
\[
\Sym\left(\frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n}  \C[z_1^{-1}, \ldots , z_n^{-1}]\right) .
\]

Consider the standard torus action $\C^\times \times \cdots \C^\times$ on $\C^n$. 
The equivariant character of local operators with respect to this symmetry is given by the plethystic exponential of the following single particle index
\[
\frac{1}{(1-q_1)\cdots (1-q_n)} .
\]
\end{eg}

@@

\subsection{Twisted global symmetry}

@@

%In \cite{SW6d} a symmetry by the exceptional super Lie algebra $E(3|6)$ on the holomorphic twist of the free tensor multiplet was constructed.
%We recall the action of its even part on local operators of the holomorphic twist of the free tensor multiplet. 
%We recount how it acts on the vector space \eqref{eqn:localfree}.
% 
%Recall that the even part of $E(3|6)$ consists of two summands:
%\[
%\Vect(\Hat{D}^3) \times \lie{sl}(2) \otimes \cO(\Hat{D}^3) .
%\]
%Formal vector fields act naturally by Lie derivative on both summands in \eqref{eqn:localfree}. 
%An $\lie{sl}(2)$-valued function acts on $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$ where we view $\C^2 = {\rm span}\{r_+,r_-\}$ as the fundamental $\lie{sl}(2)$ representation.

After complexification, the six-dimensional superconformal algebra is $\lie{osp}(8|4)$. 
The holomorphic supercharge is a supertranslation 
\[
Q \in \Pi S_+ \otimes \C^4 \subset \lie{osp}(8|4)
\]
which has the properties that $Q^2 = 0$ and that its image
\[
{\rm Im}\left(Q|_{\Pi S_+ \otimes \C^4} \right) \subset \R^6 \otimes_\R \C \cong \C^6
\]
is three-dimensional (spanned by the anti-holomorphic translations). 
The supercharge $Q$ acts on $\lie{osp}(8|4)$ by commutator, and its cohomology will automatically act on the holomorphic twist of any six-dimensional superconformal field theory. 
This cohomology can be identified with the subalgebra $\lie{osp}(6|2)$, see \cite{SWe36}.

We consider the symmetry of the holomorphic twist of a six-dimensional superconormal theory with respect to the even subalgebra 
\[
\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2) .
\]

which acts in the following way: 
\begin{itemize}
\item The Lie algebra $\lie{sl}(3)$ is a subalgebra of $\Vect(\Hat{D}^3)$ consisting of linear coefficient vector fields $\sum_{i,j} a_{ij} z_i \frac{\del}{\del z_j}.$
where $(a_{ij}) \in \lie{sl}(3)$. 
\item The Lie algebra $\lie{sl}(2)$ is the subalgebra of $\lie{sl}(2) \otimes \cO(\Hat{D}^3)$ consisting of constant formal series. 
\item The one-dimensional Lie algebra $\lie{gl}(1)$ is spanned by Euler vector field $\sum_i z_i \frac{\del}{\del z_i} \in \Vect(\Hat{D}^3).$
\end{itemize}

@@

The theory on a single fivebrane is free and the underlying cochain complex of the abelian holomorphic local Lie algebra on $\C^3$ is given by 
\beqn
\begin{tikzcd}
\ul{-1} & \ul{0} \\
\Omega^{2,\bu}(\C^3) \ar[r,"\del"] & \Omega^{3,\bu}(\C^3) \\
\Pi \Omega^{0,\bu}(\C^3, K_{\C^3}^{1/2} \otimes \C^2) . 
\end{tikzcd} 
\eeqn
Here we recall the $\Z \times \Z/2$ bigrading where the differential has bidegree $(1,0)$.

\begin{lem}
\label{lem:single}
The $\Z \times \Z/2$ algebra of local operators of the holomorphic single fivebrane theory is quasi-isomorphic to the graded symmetric algebra on the linear dual of the topological vector space
\beqn\label{eqn:localfree}
\Omega^{2}_{cl} (\Hat{D}^3)[1] \oplus \Pi \Omega^0(\Hat{D}^3, K^{1/2}) \otimes \C^2 [1].
\eeqn
\end{lem}

\begin{proof}
The jet expansion at $0 \in \C^3$ determines a map from the section of the abelian holomorphic-topological local Lie algebra on $\C^3$ to the cochain complex
\beqn
\begin{tikzcd}
\ul{-1} & \ul{0} \\
\Omega^{2}(\Hat{D}^3) \ar[r,"\del"] & \Omega^{3}(\Hat{D}^3) \\
\Pi \Omega^0(\Hat{D}^3, K^{1/2} \otimes \C^2) . 
\end{tikzcd} 
\eeqn
On the formal disk all closed two-forms are automatically exact, which implies the lemma.
\end{proof}
